GMSE: an R package for generalised management strategy evaluation

### 2018-04-18 notebook/ms/SI3.Rmd
Fix the sim calls

```{r, echo = TRUE, eval = FALSE}
sim_1 <- gmse(manager_budget = 10000, user_budget = 10000, res_death_K = 93870, 
             manage_target = 70000, RESOURCE_ini = 35000, plotting = FALSE, 
             stakeholders = 80, land_ownership = TRUE, public_land = 0.4, 
             scaring = FALSE, lambda = 0.275, remove_pr = 0.122, time_max = 40, 
             res_death_type = 3, res_consume = 0.02, res_birth_K = 200000, 
             observe_type = 3, agent_view = 1, converge_crit = 0.1);
```

```{r}
sim_1 <- gmse(time_max = 30, plotting = FALSE);
```

@@

```{r, echo = TRUE, fig.height = 6, eval = FALSE}
sim_2 <- gmse(manager_budget = 10000, user_budget = 10000, res_death_K = 93870, 
             manage_target = 70000, RESOURCE_ini = 35000, plotting = FALSE, 
             stakeholders = 80, land_ownership = TRUE, public_land = 0.4, 
             scaring = TRUE, lambda = 0.275, remove_pr = 0.122, time_max = 40, 
             res_death_type = 3, res_consume = 0.02, res_birth_K = 200000, 
             observe_type = 3, agent_view = 1, converge_crit = 0.1);
```

>>>>

```{r, echo = TRUE, eval = FALSE}
sim_1 <- gmse(manager_budget = 10000, user_budget = 10000, res_death_K = 93870, 
             manage_target = 70000, RESOURCE_ini = 35000, plotting = FALSE, 
             stakeholders = 80, land_ownership = TRUE, public_land = 0.4, 
             scaring = FALSE, lambda = 0.275, remove_pr = 0.122, time_max = 30, 
             res_death_type = 3, res_consume = 0.02, res_birth_K = 200000, 
             observe_type = 3, agent_view = 1, converge_crit = 0.01, 
             ga_mingen = 200);
```

```{r, echo = FALSE, eval = TRUE}
load("data/SI3-cull_sim.rda"); # Avoids long compiling time
sim_1 <- sim;
```

@@

```{r, echo = TRUE, fig.height = 6, eval = FALSE}
sim_2 <- gmse(manager_budget = 10000, user_budget = 10000, res_death_K = 93870, 
             manage_target = 70000, RESOURCE_ini = 35000, plotting = FALSE, 
             stakeholders = 80, land_ownership = TRUE, public_land = 0.4, 
             scaring = TRUE, lambda = 0.275, remove_pr = 0.122, time_max = 30, 
             res_death_type = 3, res_consume = 0.02, res_birth_K = 200000, 
             observe_type = 3, agent_view = 1, converge_crit = 0.01, 
             ga_mingen = 200);
```
